---
title: 'Analytic Homework #2'
author: "Mondae Atughonu"
date: "2/2/2022"
output: html_document
---


```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
```

```{r libraries}
library(tidyverse)         # for graphing and data cleaning
theme_set(theme_minimal()) # Lisa's favorite theme
```

## Project ideas

Answer the following questions to start thinking about the project.

-   What are some topics (or a single topic) you are interested in studying from a data science perspective? These can be very specific or more general.  

-   The main topic I would like to explore would be inventory management systems, specifically focusing on consumption and par adjustments based on trended data.

-   Given your to topic(s), where would you find data about it? Provide at least two sources, being as specific as possible. If you need to collect/scrape it yourself, describe the steps you'd need too take.

-  I could find data through our internal inventory system at my job or find data sources from inventory ordering based on consumer data online.  I will most likely need to scrape and clean the data to remove any financial aspects of the data and focus on the main data points that affect consumption and pars.

-   What challenges do you imagine having? How might you overcome them?  

-  The main challenge is going to be the overall reliability of the data and the repeatability of the data set metrics.  To overcome this, i will definitely need to do a Gage R&R analysis on the data I use with visuals to determine if the data is valid prior to use.

-   Type your responses below and save it on Rmarkdown. 

